`respR` - An R package for the analysis of respirometry data

### 2017-11-12 manuscript/manuscript-HTML.Rmd
manuscript update

3. We demonstrate how `respR` uses novel and parallelised computing methods such as rolling regressions and kernel density estimates to reliably detect maximum, minimum and most linear sections of the data, and critical oxygen tension, $P_{crit}$.

@@

```{r}
inspect.data(squid, xcol = 2, ycol = 3, plot = FALSE, highlight = T)
```

>>>>

3. We demonstrate how `respR` uses novel computing methods such as rolling regressions and kernel density estimates to reliably detect maximum, minimum and most linear sections of the data, and critical oxygen tension, $P_{crit}$.

@@

```{r}
inspect.data(squid, plot = F)
```
